\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage{amsmath, amsthm, amsfonts}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}

\usepackage{letltxmacro, changepage}
\LetLtxMacro\oldproof\proof
\let\endoldproof\endproof
\renewenvironment{proof}[1][\proofname]
  {\begin{adjustwidth}{2em}{2em}
   \oldproof[#1]}
  {\endoldproof
   \end{adjustwidth}}

\usepackage{amssymb}
\renewcommand{\qedsymbol}{\tiny$\blacksquare$}

\usepackage{enumerate}

\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

\begin{document}
\begin{enumerate}[1.]
\item If $r$ is rational nonzero and $x$ is irrational, then $r + x$ and $rx$
      are also irrational.
      \begin{proof}
      Let $r = \frac{m}{n}$ for some $m, n \in \Z$.

      Suppose for contradiction that $rx$ is rational. Then there are some
      $a, b \in \Z$ where $rx = x\frac{m}{n} = \frac{a}{b}$. Then we have that
      $x = \frac{an}{bm} \in \Q$ which contradicts that $x$ is irrational.
      Therefore $rx$ is irrational.

      Now suppose for contradiction that $r + x$ is rational. Then there are
      some $a, b \in Z$ where $r + x = \frac{m}{n} + x = \frac{a}{b}$. Then we
      have $x = \frac{na - bm}{nb} \in Q$ which again contradicts that $x$ is
      irrational. Therefore $r + x$ is irrational.
      \end{proof}

\item There is no rational number whose square is 12.
      \begin{proof}
      We'll first consider the possibility of a rational number whose square is
      3. That is $p^2 = \frac{m^2}{n^2} = 3$ for some $m, n \in \Z$. Suppose
      for contradiction that $n$ is even - so that $n^2$ is also even. Then
      we'd have that $m^2 = 3n^2 = 6k = 2(3k)$ for some $k\in\Z$. This shows
      that $m$ is also even. But we know that a rational number can be
      represented as $\frac{m}{n}$ where $m, n \in \Z$ are not both even. Thus
      if $n$ is even we know that there can be no such rational $\frac{m}{n}$
      so that $\frac{m^2}{n^2} = 3$.

      Furthermore we know that $12 = 2^2 \cdot 3$ so that if there were a
      rational number whose square is 12, we'd have $\frac{m^2}{(2k)^2} = 3$
      for $n = 2k^2$. This shows that $n$ must be even, therefore we have there
      can be no such rational $\frac{m^2}{(2k)^2} = 3$ and thus there's no such
      rational $\frac{m^2}{k^2} = 12$.
      \end{proof}
\end{enumerate}

\end{document}
